Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/implementation.tex
more ediiiiiiiitsssss
more edits

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. Users of \sysname only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates. Since each prefix is specified separately, the \sysname compiler is able to operate over each per-prefix routing policy in parallel.

@@

\para{PG Minimization}

The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}. More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies. All minimization steps are repeated until no more progress can be made.

>>>>

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. Users of \sysname only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates. Finally, since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.

@@

%\para{PG Minimization}

%The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}. More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies. All minimization steps are repeated until no more progress can be made.

### 2016-01-29 paper/introduction.tex
more edits

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures. This does not mean that the implementation is always 
able to send traffic to its ultimate destination 
(\EG in the case of a network partition), but rather that always respects the 
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.

>>>>

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures. This does not mean that the implementation is always 
able to send traffic to its ultimate destination 
(\EG in the case of a network partition), but rather that it always respects the 
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.
